Towards a free/open-source universal-dependency treebank for Kazakh

### 2015-06-18 2015-turklang-kazdep/paper.tex
desc. corp
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@60826 72bbbca6-d526-0410-a7d9-f06f51895060

\begin{table}
  \centering
  \begin{tabular}{|l|l|r|r|r|}
    \hline
    \textbf{Document} & \textbf{Description} & \textbf{Sentences} & \textbf{Tokens} & \textbf{Avg. length}\\
    \hline
    UDHR & Legal text on human rights & - & - & - \\
    Phrasebook & Phrases from Wikitravel & 37 & 205 & 5.5 \\
    Жиырма Бесінші Сөз & Philosophical text & 34 & 525 & 15.4 \\ 
    Өлген қазан & Folk tale & 8 & 140 & 17.5 \\
    Азамат къайда? & Story for children and language learners & 48 & 434 & 9.0 \\
    Футболдан әлем чемпионаты 2014  & Wikipedia article (2014 World Cup) & 14 & 246 & 17.5 \\
    Иран & Wikipedia article (Iran) & - & - & - \\
    Радиан & Wikipedia article (Radian) & - & - & - \\
    \hline
  \end{tabular}
  \caption{Composition of the corpus. The corpus covers a range of genres and text types.}
\end{table}

>>>>

\begin{table}
  \centering
  \begin{tabular}{|l|l|r|r|r|}
    \hline
    \textbf{Document} & \textbf{Description} & \textbf{Sentences} & \textbf{Tokens} & \textbf{Avg. length}\\
    \hline
    Declaration on Human Rights & Legal text on human rights & - & - & - \\
    Phrasebook & Phrases from Wikitravel & 37 & 205 & 5.5 \\
    Жиырма Бесінші Сөз & Philosophical text & 34 & 525 & 15.4 \\ 
    Өлген қазан & Folk tale & 8 & 140 & 17.5 \\
    Азамат къайда? & Story for children and language learners & 48 & 434 & 9.0 \\
    Футболдан әлем чемпионаты 2014  & Wikipedia article (2014 World Cup) & 14 & 246 & 17.5 \\
    Иран & Wikipedia article (Iran) & - & - & - \\
    Радиан & Wikipedia article (Radian) & - & - & - \\
    \hline
  \end{tabular}
  \caption{Composition of the corpus. The corpus covers a range of genres and text types.}
\end{table}
